Mechanical loading prediction through accelerometry data during walking and running

### 2022-03-12 manuscript/manuscript.Rmd
Improve suppl figs formating
Add reference to Suppl Fig 1 and update its caption

FP and accelerometer data were processed using MATLAB (Version 2019a, Mathworks, Natick, USA), as described elsewhere [@Veras2020]. Briefly, both GRF and acceleration signals were filtered using a Butterworth fourth-order low-pass filter, with 20 Hz cut-off frequency, and their resultant vector calculated ($r_i = \sqrt{x_i^2 + y_i^2 + z_i^2}$). After that, peak ACC (pACC) values were defined as minimum height of twice the positive ACC average, during any given speed, and separated by 0.4 seconds minimum. GRF and ACC signals were adjusted through the time set by the systems clock, with manual correction based on visual inspection for possible errors, and then synchronized by the maximum cross-correlation coefficient. Peak GRF (pGRF) was determined as the highest value between 0.4 seconds before and after each pACC. The rates of change were computed through a centered derivative from the beginning of the foot contact to the peak (Equation 1). The peak loading rate (pLR) and peak acceleration rate (pAR) were defined as the maximum value in the array (Equation 2).

@@

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS1.png}
	\end{measuredfigure}
\end{figure}
\footnotesize \textbf{Supplemental Figure S1.} Example of the ground reaction force and acceleration signals during the stance phase. Signals were mean centered and scaled to units of standard deviation to fit in the same plot window. In this image, the peak of each signal (star mark) represents the maximum impact between the foot and the ground. The circles mark the beginning of the curve, i.e., the start of the ascending phase of the signal that culminates in its peak. The region of the acceleration signal between the circle and the star marks was used to compute the acceleration rate, and the same region on the ground reaction force signal was used to compute the loading rate.

>>>>

FP and accelerometer data were processed using MATLAB (Version 2019a, Mathworks, Natick, USA), as described elsewhere [@Veras2020]. Briefly, both GRF and acceleration signals were filtered using a Butterworth fourth-order low-pass filter, with 20 Hz cut-off frequency, and their resultant vector calculated ($r_i = \sqrt{x_i^2 + y_i^2 + z_i^2}$). After that, peak ACC (pACC) values were defined as minimum height of twice the positive ACC average, during any given speed, and separated by 0.4 seconds minimum. GRF and ACC signals were adjusted through the time set by the systems clock, with manual correction based on visual inspection for possible errors, and then synchronized by the maximum cross-correlation coefficient. Peak GRF (pGRF) was determined as the highest value between 0.4 seconds before and after each pACC. The rates of change were computed through a centered derivative from the beginning of the foot contact to the peak (Equation 1). The peak loading rate (pLR) and peak acceleration rate (pAR) were defined as the maximum value in the array (Equation 2). An example of GRF and ACC curves during the stance phase of both walking and running can be seen in Supplemental Figure 1.

@@

\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS1.png}
	\end{measuredfigure}
\end{figure}
\footnotesize \textbf{Supplemental Figure S1.} Example of ground reaction force and acceleration signals during the stance phase of walking (left panel) and running (right panel). Signals were mean centered and scaled to units of standard deviation to fit in the same plot window. In this image, the peak of each signal, represented by the start marks, is its maximum magnitude during the stance. The peak acceleration rate and peak loading rate were identified as the steepest part of each curve.
